---
title: "6 - Estimator robustness"
output: html_document
---

Every network in this paper is estimated with `mgm()` under EBIC (`lambdaGam = 0.25`) and the
AND rule, which are the settings `bootnet(default = "mgm")` applies internally. That choice
departs from the defaults of the `mgm` package itself, which are cross-validation for the
tuning parameter and the AND rule for combining the nodewise regressions.

This script asks whether the departure matters. It repeats the entire H1 and H2 analysis,
bootstraps and difference tests included, under two alternative specifications:

- **CV, AND**, the `mgm` package default. Only the tuning criterion changes, so this
  isolates the effect of the criterion.
- **CV, OR**, cross-validation with the OR rule. This is the setting used to draw the
  network figures in the originally submitted version of the manuscript, kept here so the
  record is complete.

The output is Table S10 of the Supplement: the verdict for each of the 34 country-networks
under all three specifications.

# Input

```{r}
library(pacman)
p_load(tidyverse, here, mgm, bootnet, huge, conflicted, sjPlot)

rm(list = ls())
options(scipen = 999)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)

master_datasets <- readRDS(here("Input", "Secondary", "master_datasets.rds"))

out_dir <- here("Output", "Estimator_Robustness")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

alt_file <- here("Input", "Secondary", "boot_alt_master.rds")

# The bootstraps below take roughly 70 minutes per specification on 16 cores, so they are
# not run by default: boot_alt_master.rds ships with the repository. Set this to TRUE to
# re-run them from scratch.
RUN_BOOTSTRAPS <- FALSE
```

# Matrices

```{r}
# Identical construction to scripts 3 and 4, so the networks are the same objects.
# The summary node (CM in H1, CB in H2) is always the first column.
H1_matrices <- list()
H2_matrices <- list()

for (study_name in names(master_datasets)) {
  df <- master_datasets[[study_name]]

  df_h1 <- df %>% select(country, CM, starts_with("cb_")) %>% na.omit()
  split_h1 <- split(df_h1[, setdiff(names(df_h1), "country")], df_h1$country)
  for (cn in names(split_h1)) {
    H1_matrices[[paste0(study_name, "_", cn)]] <-
      huge.npn(as.matrix(split_h1[[cn]]), verbose = FALSE)
  }

  df_h2 <- df %>% select(country, CB, starts_with("cm_")) %>% na.omit()
  split_h2 <- split(df_h2[, setdiff(names(df_h2), "country")], df_h2$country)
  for (cn in names(split_h2)) {
    H2_matrices[[paste0(study_name, "_", cn)]] <-
      huge.npn(as.matrix(split_h2[[cn]]), verbose = FALSE)
  }
}

cat("H1 networks:", length(H1_matrices), " H2 networks:", length(H2_matrices), "\n")
```

# Bootstraps under the alternative specifications

```{r}
SPECS <- list(
  CV_AND = list(criterion = "CV", rule = "AND"),
  CV_OR  = list(criterion = "CV", rule = "OR")
)

if (RUN_BOOTSTRAPS) {

  boot_alt <- list()

  for (spec_name in names(SPECS)) {
    spec <- SPECS[[spec_name]]
    boot_alt[[spec_name]] <- list()

    for (hyp in c("H1", "H2")) {
      mats <- if (hyp == "H1") H1_matrices else H2_matrices
      boot_alt[[spec_name]][[hyp]] <- list()

      for (nm in names(mats)) {
        cat(spec_name, hyp, nm, "...\n")
        # Seeded per network so a single network can be re-run on its own and reproduce.
        set.seed(123)
        boot_alt[[spec_name]][[hyp]][[nm]] <- bootnet(
          mats[[nm]],
          nBoots     = 1000,
          nCores     = 16,
          default    = "mgm",
          criterion  = spec$criterion,
          rule       = spec$rule,
          statistics = "strength",
          verbose    = FALSE
        )
      }
    }
  }

  saveRDS(boot_alt, alt_file)
}

boot_alt <- readRDS(alt_file)
```

# Difference tests

```{r}
# The same decision rule as script 7, applied unchanged to each alternative specification.
#
#   supported    = the summary node is reliably MORE central than every other node
#   falsified    = the summary node is reliably LESS central than every other node
#   inconclusive = neither

diff_test <- function(boot_list, hyp) {
  map_dfr(names(boot_list), function(nm) {

    x  <- boot_list[[nm]]
    lb <- x$sample$labels
    summ <- lb[1]

    bt <- x$bootTable
    stopifnot(all(as.character(bt$node1) == rep(lb, length.out = nrow(bt))))

    M <- matrix(bt$value, ncol = length(lb), byrow = TRUE)
    colnames(M) <- lb

    others <- setdiff(lb, summ)
    d  <- vapply(others, function(o) quantile(M[, summ] - M[, o], c(.025, .975)),
                 numeric(2))

    st <- colSums(abs(x$sample$graph)); names(st) <- lb

    data.frame(
      Hypothesis    = hyp,
      Network       = nm,
      Summary_node  = summ,
      N_nodes       = length(lb),
      Strength      = round(unname(st[summ]), 3),
      CI_lower      = round(unname(quantile(M[, summ], .025)), 3),
      CI_upper      = round(unname(quantile(M[, summ], .975)), 3),
      Rank          = as.integer(rank(-st)[1]),
      N_sig_higher  = sum(d[1, ] > 0),
      N_sig_lower   = sum(d[2, ] < 0),
      N_comparisons = length(others),
      Sig_highest   = all(d[1, ] > 0),
      Sig_lowest    = all(d[2, ] < 0),
      stringsAsFactors = FALSE
    )
  })
}

verdict_of <- function(df) {
  df %>% mutate(Verdict = case_when(Sig_highest ~ "supported",
                                    Sig_lowest  ~ "falsified",
                                    TRUE        ~ "inconclusive"))
}

alt_results <- map_dfr(names(SPECS), function(spec_name) {
  bind_rows(
    diff_test(boot_alt[[spec_name]][["H1"]], "H1"),
    diff_test(boot_alt[[spec_name]][["H2"]], "H2")
  ) %>% verdict_of() %>% mutate(Spec = spec_name)
})

# The main specification, straight from the bootstraps used in the article.
boot_results_H1 <- readRDS(here("Input", "Secondary", "boot_H1_master.rds"))
boot_results_H2 <- readRDS(here("Input", "Secondary", "boot_H2_master.rds"))

main_results <- bind_rows(diff_test(boot_results_H1, "H1"),
                          diff_test(boot_results_H2, "H2")) %>%
  verdict_of() %>% mutate(Spec = "EBIC_AND")

all_results <- bind_rows(main_results, alt_results)
write.csv(all_results, file.path(out_dir, "Estimator_Robustness_Full.csv"), row.names = FALSE)
```

# Comparison

```{r}
wide <- all_results %>%
  select(Hypothesis, Network, Summary_node, Spec, Strength, CI_lower, CI_upper, Rank, Verdict) %>%
  pivot_wider(names_from = Spec,
              values_from = c(Strength, CI_lower, CI_upper, Rank, Verdict))

wide <- wide %>%
  mutate(
    Verdicts_identical = Verdict_EBIC_AND == Verdict_CV_AND &
                         Verdict_EBIC_AND == Verdict_CV_OR,
    Ranks_identical    = Rank_EBIC_AND == Rank_CV_AND &
                         Rank_EBIC_AND == Rank_CV_OR
  )

cat("Networks:", nrow(wide), "\n")
cat("Verdict identical across all three specifications:", sum(wide$Verdicts_identical), "\n")
cat("Summary-node rank identical across all three specifications:", sum(wide$Ranks_identical), "\n")

cat("\nDisagreements, if any:\n")
wide %>% filter(!Verdicts_identical) %>%
  select(Hypothesis, Network, Verdict_EBIC_AND, Verdict_CV_AND, Verdict_CV_OR) %>%
  as.data.frame() %>% print()

write.csv(wide, file.path(out_dir, "Estimator_Robustness_Comparison.csv"), row.names = FALSE)
```

```{r}
# Table S10, formatted for the Supplement.
# as.data.frame(check.names = FALSE) at the end matters: tab_df() sanitises the column names
# of a tibble, which turns "EBIC, AND (main)" into "EBIC..AND..main.".
table_S10 <- wide %>%
  transmute(
    Hypothesis,
    Network,
    `Summary node` = Summary_node,
    `EBIC, AND (main)` = sprintf("%.2f [%.2f, %.2f], %s",
                                 Strength_EBIC_AND, CI_lower_EBIC_AND, CI_upper_EBIC_AND,
                                 Verdict_EBIC_AND),
    `CV, AND` = sprintf("%.2f [%.2f, %.2f], %s",
                        Strength_CV_AND, CI_lower_CV_AND, CI_upper_CV_AND, Verdict_CV_AND),
    `CV, OR`  = sprintf("%.2f [%.2f, %.2f], %s",
                        Strength_CV_OR, CI_lower_CV_OR, CI_upper_CV_OR, Verdict_CV_OR),
    Agreement = ifelse(Verdicts_identical, "yes", "no")
  ) %>%
  as.data.frame(check.names = FALSE)

# tab_df() sanitises the column names it is given and tab_dfs() does not, so the table goes
# through tab_dfs() as a one-element list and its HTML is written here. This is the same route
# Tables S2, S5 and S8 take in script 8.
s10 <- tab_dfs(
  list(table_S10),
  titles = paste("Table S10: estimator robustness. Strength of the summary node with its",
                 "95% bootstrap interval and the verdict of the difference test, under the",
                 "specification used in the article (EBIC, lambdaGam = 0.25, AND rule) and",
                 "under two alternatives that select the tuning parameter by",
                 "cross-validation. Each cell rests on 1,000 non-parametric bootstraps.")
)
target_s10 <- file.path(out_dir, "Table_S10_Estimator_Robustness.doc")
writeLines(s10$page.complete, con = file(target_s10, encoding = "UTF-8"))
stopifnot(file.exists(target_s10))

table_S10
```

```{r}
# Counts as they would be stated in the Supplement.
all_results %>% count(Spec, Hypothesis, Verdict) %>% as.data.frame() %>% print()
```
