---
title: "7 - Reporting checks"
output: html_document
---

This script exists for one reason: every number we put in the Results has to be re-derivable
from the data without reading it off a figure. It recomputes the sample sizes, the EGA
communities, the reliability and fit statistics with their intervals, and above all the
bootstrapped difference tests on Strength that decide H1 and H2 in each country-network. It
also re-estimates all the H1/H2 networks under cross-validation as a quick check on the tuning
criterion; script 6 carries the full version of that check, with bootstraps and difference
tests under two alternative specifications.

# Input

```{r}
library(pacman)
p_load(tidyverse, here, psych, lavaan, EGAnet, mgm, bootnet, huge, conflicted, sjPlot)

rm(list = ls())
options(scipen = 999)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)

# master_datasets.rds is built by script 1 and is included in this repository, so this script
# runs as-is. The raw Study 2 and Study 3 files that script 1 starts from are not redistributed
# here: see the note at the top of 1_Data_Managment.Rmd, or "Data sources" in the README,
# for how to download them from the Harvard Dataverse.
master_datasets <- readRDS(here("Input", "Secondary", "master_datasets.rds"))
boot_results_H1 <- readRDS(here("Input", "Secondary", "boot_H1_master.rds"))
boot_results_H2 <- readRDS(here("Input", "Secondary", "boot_H2_master.rds"))

out_dir <- here("Output", "Reporting_Checks")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Sample sizes

```{r}
# These are the Ns actually analysed, i.e. after listwise deletion on the items used.
# The raw CCRS file has 8,101 respondents, but the Study 3 analytic sample is smaller.
n_table <- map_dfr(names(master_datasets), function(s) {
  d <- master_datasets[[s]] %>%
    select(country, starts_with("cm_"), starts_with("cb_")) %>%
    na.omit()
  d %>% count(country) %>% mutate(Study = s)
}) %>% select(Study, country, n)

n_table
n_table %>% group_by(Study) %>% summarise(N = sum(n))
cat("Total analytic N:", sum(n_table$n), "\n")

write.csv(n_table, file.path(out_dir, "Check_Sample_Sizes.csv"), row.names = FALSE)
```

# Matrices

```{r}
H1_matrices <- list()
H2_matrices <- list()
H0_matrices <- list()

for (study_name in names(master_datasets)) {
  df <- master_datasets[[study_name]]

  d0 <- df %>% select(country, starts_with("cm_"), starts_with("cb_")) %>% na.omit()
  for (cn in unique(d0$country)) {
    H0_matrices[[paste0(study_name, "_", cn)]] <-
      as.matrix(d0[d0$country == cn, setdiff(names(d0), "country")])
  }

  d1 <- df %>% select(country, CM, starts_with("cb_")) %>% na.omit()
  for (cn in unique(d1$country)) {
    H1_matrices[[paste0(study_name, "_", cn)]] <-
      huge.npn(as.matrix(d1[d1$country == cn, setdiff(names(d1), "country")]), verbose = FALSE)
  }

  d2 <- df %>% select(country, CB, starts_with("cm_")) %>% na.omit()
  for (cn in unique(d2$country)) {
    H2_matrices[[paste0(study_name, "_", cn)]] <-
      huge.npn(as.matrix(d2[d2$country == cn, setdiff(names(d2), "country")]), verbose = FALSE)
  }
}
```

# H0: EGA communities

```{r}
ega_check <- map_dfr(names(H0_matrices), function(nm) {
  e <- suppressWarnings(EGA(H0_matrices[[nm]], plot.EGA = FALSE))
  wc <- e$wc
  data.frame(
    Network      = nm,
    N_communities = length(unique(wc[!is.na(wc)])),
    N_unassigned  = sum(is.na(wc)),
    Partition     = paste(paste0(names(wc), ":", wc), collapse = " "),
    stringsAsFactors = FALSE
  )
})

ega_check %>% select(Network, N_communities, N_unassigned)
write.csv(ega_check, file.path(out_dir, "Check_EGA_Communities.csv"), row.names = FALSE)
```

# Reliability and fit, with intervals

```{r}
ci_check <- map_dfr(names(H0_matrices), function(nm) {
  d  <- as.data.frame(H0_matrices[[nm]])
  cm <- d[, grepl("^cm_", names(d)), drop = FALSE]
  cb <- d[, grepl("^cb_", names(d)), drop = FALSE]

  a_cm <- suppressWarnings(psych::alpha(cm))
  a_cb <- suppressWarnings(psych::alpha(cb))

  mod <- paste0("Factor1_CB =~ ", paste(names(cb), collapse = " + "), "\n",
                "Factor2_CM =~ ", paste(names(cm), collapse = " + "))
  fit <- suppressWarnings(cfa(mod, data = d, std.lv = TRUE))
  fm  <- fitMeasures(fit, c("chisq", "df", "cfi", "tli",
                            "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr", "bic"))

  # unname() matters: psych and lavaan return named numerics, and data.frame() would
  # otherwise overwrite my column names with theirs.
  data.frame(
    Network = nm, N = nrow(d),
    Alpha_CM = round(unname(a_cm$total$raw_alpha), 3),
    Alpha_CM_LCI = round(unname(a_cm$feldt$lower.ci), 3),
    Alpha_CM_UCI = round(unname(a_cm$feldt$upper.ci), 3),
    Alpha_CB = round(unname(a_cb$total$raw_alpha), 3),
    Alpha_CB_LCI = round(unname(a_cb$feldt$lower.ci), 3),
    Alpha_CB_UCI = round(unname(a_cb$feldt$upper.ci), 3),
    CFI = round(unname(fm["cfi"]), 3), TLI = round(unname(fm["tli"]), 3),
    RMSEA = round(unname(fm["rmsea"]), 3),
    RMSEA_LCI = round(unname(fm["rmsea.ci.lower"]), 3),
    RMSEA_UCI = round(unname(fm["rmsea.ci.upper"]), 3),
    SRMR = round(unname(fm["srmr"]), 3), BIC = round(unname(fm["bic"]), 2),
    stringsAsFactors = FALSE
  )
})

ci_check
write.csv(ci_check, file.path(out_dir, "Check_Alpha_Fit_CIs.csv"), row.names = FALSE)
```

# H1 and H2: rank of the summary node

```{r}
# The summary node (CM in H1, CB in H2) is always the first column of the matrix.
# I take three things per network: the rank of its point estimate in the bootnet sample
# network, whether its 95% bootstrap CI sits entirely above or entirely below the CIs of all
# the other nodes, and the same rank recomputed with the CV/OR settings used for the plots.

rank_from_boot <- function(boot_list, hyp) {
  map_dfr(names(boot_list), function(nm) {
    x  <- boot_list[[nm]]
    lb <- x$sample$labels
    st <- colSums(abs(x$sample$graph)); names(st) <- lb

    bt <- x$bootTable
    stopifnot(all(as.character(bt$node1) == rep(lb, length.out = nrow(bt))))

    ci <- bt %>%
      group_by(node1) %>%
      summarise(lo = quantile(value, .025), hi = quantile(value, .975), .groups = "drop")
    ci <- ci[match(lb, ci$node1), ]

    data.frame(
      Hypothesis   = hyp,
      Network      = nm,
      N_nodes      = length(st),
      Summary_node = lb[1],
      Rank         = as.integer(rank(-st)[1]),
      Is_highest   = st[1] == max(st),
      Is_lowest    = st[1] == min(st),
      CI_lower     = round(ci$lo[1], 3),
      CI_upper     = round(ci$hi[1], 3),
      CI_above_all = ci$lo[1] > max(ci$hi[-1]),
      CI_below_all = ci$hi[1] < min(ci$lo[-1]),
      stringsAsFactors = FALSE
    )
  })
}

ranks_boot <- bind_rows(rank_from_boot(boot_results_H1, "H1"),
                        rank_from_boot(boot_results_H2, "H2"))
ranks_boot
```

```{r}
# The same ranks, re-derived from point estimates under cross-validation and the OR rule,
# which is a setting no figure in the paper uses.
# Everything in the paper, drawn or analysed, uses EBIC (lambdaGam = 0.25) with the AND rule,
# which is what bootnet(default = "mgm") applies. This block is the cheap version of the
# tuning check: it compares point-estimate ranks only. Script 6 runs the full version,
# bootstrapping each alternative specification and re-running the difference tests.
set.seed(123)

rank_cv <- function(mat_list, hyp) {
  map_dfr(names(mat_list), function(nm) {
    m <- mat_list[[nm]]; k <- ncol(m)
    fit <- mgm(m, type = rep("g", k), level = rep(1, k),
               lambdaSel = "CV", ruleReg = "OR", verbose = FALSE, pbar = FALSE)
    st <- colSums(abs(fit$pairwise$wadj)); names(st) <- colnames(m)
    data.frame(Hypothesis = hyp, Network = nm,
               Rank_CV = as.integer(rank(-st)[1]),
               stringsAsFactors = FALSE)
  })
}

ranks_cv <- bind_rows(rank_cv(H1_matrices, "H1"), rank_cv(H2_matrices, "H2"))

ranks_all <- left_join(ranks_boot, ranks_cv, by = c("Hypothesis", "Network")) %>%
  mutate(Same_rank = Rank == Rank_CV)

ranks_all
cat("Networks where CV/OR and EBIC/AND give a different rank:",
    sum(!ranks_all$Same_rank), "out of", nrow(ranks_all), "\n")

write.csv(ranks_all, file.path(out_dir, "Check_Summary_Node_Ranks.csv"), row.names = FALSE)
```

# Bootstrapped difference tests on Strength

```{r}
# This is the decision rule the paper applies to H1 and H2.
#
# Comparing point estimates ("the summary node has the highest Strength") is not a test, and
# comparing two marginal bootstrap CIs is not one either: two nodes can differ reliably while
# their intervals overlap, so a non-overlap rule is conservative in a direction we cannot
# quantify. Epskamp, Borsboom & Fried (2018) recommend the bootstrapped difference test, which
# is what we use: for every other node in the network, take the difference in Strength within
# each bootstrap sample and read the 2.5th and 97.5th percentiles of that difference.
#
# The summary node (CM in H1, CB in H2) is always the first column of the input matrix.
#   supported   = the summary node is reliably MORE central than every other node
#   falsified   = the summary node is reliably LESS central than every other node
#   inconclusive = neither

diff_test <- function(boot_list, hyp) {
  map_dfr(names(boot_list), function(nm) {

    x  <- boot_list[[nm]]
    lb <- x$sample$labels
    summ <- lb[1]

    bt <- x$bootTable
    stopifnot(all(as.character(bt$node1) == rep(lb, length.out = nrow(bt))))

    # bootTable arrives in blocks of length(lb) rows, one block per bootstrap sample,
    # in the column order of the input matrix (asserted just above).
    M <- matrix(bt$value, ncol = length(lb), byrow = TRUE)
    colnames(M) <- lb

    others <- setdiff(lb, summ)
    d  <- vapply(others, function(o) quantile(M[, summ] - M[, o], c(.025, .975)),
                 numeric(2))

    st <- colSums(abs(x$sample$graph)); names(st) <- lb

    data.frame(
      Hypothesis    = hyp,
      Network       = nm,
      Summary_node  = summ,
      N_nodes       = length(lb),
      Strength      = round(unname(st[summ]), 3),
      CI_lower      = round(unname(quantile(M[, summ], .025)), 3),
      CI_upper      = round(unname(quantile(M[, summ], .975)), 3),
      Rank          = as.integer(rank(-st)[1]),
      N_sig_higher  = sum(d[1, ] > 0),
      N_sig_lower   = sum(d[2, ] < 0),
      N_comparisons = length(others),
      Sig_highest   = all(d[1, ] > 0),
      Sig_lowest    = all(d[2, ] < 0),
      stringsAsFactors = FALSE
    )
  })
}

diff_all <- bind_rows(diff_test(boot_results_H1, "H1"),
                      diff_test(boot_results_H2, "H2")) %>%
  mutate(Verdict = case_when(Sig_highest ~ "supported",
                             Sig_lowest  ~ "falsified",
                             TRUE        ~ "inconclusive"))

diff_all
write.csv(diff_all, file.path(out_dir, "Check_Difference_Tests.csv"), row.names = FALSE)
```

```{r}
# The same table, formatted for the Supplement (Table S9).
table_S9 <- diff_all %>%
  transmute(
    Hypothesis,
    Network,
    `Summary node`      = Summary_node,
    Strength            = sprintf("%.2f [%.2f, %.2f]", Strength, CI_lower, CI_upper),
    Rank,
    `Sig. higher than`  = sprintf("%d/%d", N_sig_higher, N_comparisons),
    `Sig. lower than`   = sprintf("%d/%d", N_sig_lower,  N_comparisons),
    Verdict
  )

dir.create(here("Output", "Difference_Tests"), recursive = TRUE, showWarnings = FALSE)
tab_df(table_S9,
       title = paste("Table S9: bootstrapped difference tests on Strength.",
                     "A hypothesis is supported only where the summary node is reliably more",
                     "central than every other node, and falsified where it is reliably less",
                     "central than every other node."),
       file = here("Output", "Difference_Tests", "Table_S9_Difference_Tests.doc"))
```

```{r}
# Counts as they are stated in the Results.
diff_all %>% count(Hypothesis, Verdict) %>% print()

cat("
Supported networks:
")
diff_all %>% filter(Verdict == "supported") %>% select(Hypothesis, Network) %>% print()

cat("
Per study:
")
diff_all %>%
  mutate(Study = case_when(grepl("Study1", Network) ~ "Study 1",
                           grepl("Study2", Network) ~ "Study 2",
                           TRUE                     ~ "Study 3")) %>%
  count(Study, Hypothesis, Verdict) %>% as.data.frame() %>% print()
```

# The sentences these numbers have to support

```{r}
# Study 1, H1: in how many countries is the mentality index the least central node?
ranks_all %>% filter(Hypothesis == "H1", grepl("Study1", Network)) %>%
  summarise(lowest = sum(Is_lowest), ci_below_all = sum(CI_below_all)) %>% print()
ranks_all %>% filter(Hypothesis == "H1", grepl("Study1", Network), !Is_lowest) %>%
  select(Network, Rank, N_nodes) %>% print()

# Study 1, H2: in which countries is the beliefs index the most central node?
ranks_all %>% filter(Hypothesis == "H2", grepl("Study1", Network)) %>%
  select(Network, Rank, Is_highest, CI_above_all) %>% print()

# Study 3, H1: least central everywhere, CI below all others where?
ranks_all %>% filter(Hypothesis == "H1", grepl("Study3", Network)) %>%
  select(Network, Rank, Is_lowest, CI_below_all) %>% print()

# Study 3, H2: the beliefs index is the least central node in every country
ranks_all %>% filter(Hypothesis == "H2", grepl("Study3", Network)) %>%
  select(Network, Rank, Is_lowest) %>% print()
```

# CS coefficients

```{r}
cs <- read.csv(here("Output", "Robustness", "Stability", "Appendix_CS_Coefficients.csv"),
               stringsAsFactors = FALSE)

cs %>%
  mutate(Hyp = substr(Network, 1, 2),
         Study = case_when(grepl("Study1", Network) ~ "Study 1",
                           grepl("Study2", Network) ~ "Study 2",
                           TRUE ~ "Study 3")) %>%
  group_by(Study, Hyp) %>%
  summarise(min_CS = min(CS_Coefficient),
            where  = Network[which.min(CS_Coefficient)], .groups = "drop")
```
