---
title: "8 - Export the submission bundle"
output: html_document
---

The analysis scripts write their output under names that describe what produced it
(`H1_Study1_Composite_A.png`). The journal, the co-authors and anyone checking the paper
against this repository need the opposite: names that match what the article calls things.

This script builds `Output/Submission/`, in which every file carries the name it has in the
article or the Supplement. Nothing is recomputed here. Two tables are assembled rather than
copied, because Tables S2, S5 and S8 each combine a reliability panel and a fit panel that
the analysis scripts write as one master file across all three studies.

Run it last, after scripts 2, 3, 4, 5, 6 and 7.

# Input

```{r}
library(pacman)
p_load(tidyverse, here, sjPlot, conflicted)

rm(list = ls())
options(scipen = 999)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)

sub_dir <- here("Output", "Submission")
if (dir.exists(sub_dir)) unlink(sub_dir, recursive = TRUE)
dir.create(sub_dir, recursive = TRUE, showWarnings = FALSE)

# Every copy is checked. A silent failure here would ship a bundle with a figure missing,
# which is exactly the class of error this script exists to prevent.
copied <- character(0)
missing <- character(0)

put <- function(from, to) {
  src <- here(from)
  if (!file.exists(src)) {
    missing <<- c(missing, from)
    return(invisible(FALSE))
  }
  ok <- file.copy(src, file.path(sub_dir, to), overwrite = TRUE)
  if (ok) copied <<- c(copied, to) else missing <<- c(missing, from)
  invisible(ok)
}
```

# Article figures

```{r}
put(file.path("Output", "Figures", "Figure 1 - conspiracy belief systems in the U.S.png"), "Figure 1.png")
put(file.path("Output", "Figures", "Figure 2 - Study 1 results.png"),                      "Figure 2.png")
put(file.path("Output", "Figures", "Figure 3 - Study 2 results.png"),                      "Figure 3.png")
put(file.path("Output", "Figures", "Figure 4 - Study 3 results.png"),                      "Figure 4.png")

# The vector versions are what the publisher typesets from.
put(file.path("Output", "Figures", "Figure_1.pdf"), "Figure 1.pdf")
put(file.path("Output", "Figures", "Figure_2.pdf"), "Figure 2.pdf")
put(file.path("Output", "Figures", "Figure_3.pdf"), "Figure 3.pdf")
put(file.path("Output", "Figures", "Figure_4.pdf"), "Figure 4.pdf")
```

# Supplement figures

```{r}
H0c <- file.path("Output", "H0", "Composite_Figures")
H1c <- file.path("Output", "H1", "Composite_Figures")
H2c <- file.path("Output", "H2", "Composite_Figures")
RB  <- file.path("Output", "Robustness")
ST  <- file.path("Output", "Robustness", "Stability")
MC  <- file.path("Output", "Robustness", "MC")

# Study 1
put(file.path(H0c, "H0_Study1_Composite_A.png"), "Figure S1.png")
put(file.path(H0c, "H0_Study1_Composite_B.png"), "Figure S2.png")
put(file.path(H1c, "H1_Study1_Composite_A.png"), "Figure S3.png")
put(file.path(H1c, "H1_Study1_Composite_B.png"), "Figure S4.png")
put(file.path(H2c, "H2_Study1_Composite_A.png"), "Figure S5.png")
put(file.path(H2c, "H2_Study1_Composite_B.png"), "Figure S6.png")
put(file.path(RB, "Centrality_Profiles_Study1_SUSPECTS.png"), "Figure S7.png")
put(file.path(ST, "Panel_Study1_SUSPECTS_H1.png"),            "Figure S8.png")
put(file.path(ST, "Panel_Study1_SUSPECTS_H2.png"),            "Figure S9.png")

# Study 2
put(file.path(H0c, "H0_Study2_Composite.png"), "Figure S10.png")
put(file.path(H1c, "H1_Study2_Composite.png"), "Figure S11.png")
put(file.path(H2c, "H2_Study2_Composite.png"), "Figure S12.png")
put(file.path(RB, "Centrality_Profiles_Study2_ACTS.png"),     "Figure S13.png")
put(file.path(ST, "Panel_Study2_ACTS_All_Hypotheses.png"),    "Figure S14.png")

# Study 3
put(file.path(H0c, "H0_Study3_CMQ_Composite_A.png"), "Figure S15.png")
put(file.path(H0c, "H0_Study3_CMQ_Composite_B.png"), "Figure S16.png")
put(file.path(H1c, "H1_Study3_CMQ_Composite_A.png"), "Figure S17.png")
put(file.path(H1c, "H1_Study3_CMQ_Composite_B.png"), "Figure S18.png")
put(file.path(H2c, "H2_Study3_CMQ_Composite_A.png"), "Figure S19.png")
put(file.path(H2c, "H2_Study3_CMQ_Composite_B.png"), "Figure S20.png")
put(file.path(RB, "Centrality_Profiles_Study3_CMQ.png"), "Figure S21.png")
put(file.path(ST, "Panel_Study3_CMQ_H1.png"),           "Figure S22.png")
put(file.path(ST, "Panel_Study3_CMQ_H2.png"),           "Figure S23.png")

# Equal-item Monte Carlo
put(file.path(MC, "MC_Final_Hub_Probability.png"),    "Figure S24.png")
put(file.path(MC, "MC_Final_Delta_Mean_Violin.png"),  "Figure S25.png")
```

# Supplement tables that are copied

```{r}
WD <- file.path("Output", "Wording")

put(file.path(WD, "Table_S1_Wording_Study1.doc"), "Table S1.doc")
put(file.path(WD, "Table_S3_Wording_Study2.doc"), "Table S3.doc")
put(file.path(WD, "Table_S6_Wording_Study3.doc"), "Table S6.doc")

put(file.path("Output", "H0", "Robustness", "Study2_Dimensionality_Check.doc"),     "Table S4.doc")
put(file.path("Output", "H0", "Robustness", "Table_S7_Canada_US_Comparison.doc"),   "Table S7.doc")
put(file.path("Output", "Difference_Tests", "Table_S9_Difference_Tests.doc"),       "Table S9.doc")
put(file.path("Output", "Estimator_Robustness", "Table_S10_Estimator_Robustness.doc"), "Table S10.doc")
```

# Supplement tables that are assembled

```{r}
# Tables S2, S5 and S8 have the same shape and differ only in which study they cover:
# a reliability panel with Feldt 95% intervals on alpha, and a two-factor CFA fit panel
# with the 90% RMSEA interval. The analysis writes one master file per quantity across all
# three studies, so the per-study tables are cut here.

alpha_master <- read.csv(here("Output", "H0", "Alpha_Reliability_Master.csv"),
                         stringsAsFactors = FALSE)
fit_master   <- read.csv(here("Output", "H0", "CFA_Fit_Stats_Master.csv"),
                         stringsAsFactors = FALSE)
ci_master    <- read.csv(here("Output", "H0", "Alpha_RMSEA_CIs.csv"),
                         stringsAsFactors = FALSE)

short_name <- function(x) {
  x <- sub("^Study1_SUSPECTS_", "", x)
  x <- sub("^Study2_ACTS_",     "", x)
  x <- sub("^Study3_CMQ_",      "", x)
  x
}

# ci is the one that carries both alpha and its interval, so the reliability panel is built
# from it and the item counts are joined in from the alpha master.
build_reliability <- function(prefix) {
  ci  <- ci_master[grepl(prefix, ci_master$Dataset, fixed = TRUE), , drop = FALSE]
  alp <- alpha_master[grepl(prefix, alpha_master$Dataset, fixed = TRUE), , drop = FALSE]
  m   <- merge(ci, alp[, c("Dataset", "CM_Items", "CB_Items")], by = "Dataset", sort = FALSE)
  data.frame(
    Dataset                   = short_name(m$Dataset),
    N                         = m$N,
    `CM items`                = m$CM_Items,
    `Alpha (CM) [95% CI]`     = sprintf("%.2f [%.2f, %.2f]", m$Alpha_CM, m$Alpha_CM_LCI, m$Alpha_CM_UCI),
    `CB items`                = m$CB_Items,
    `Alpha (CB) [95% CI]`     = sprintf("%.2f [%.2f, %.2f]", m$Alpha_CB, m$Alpha_CB_LCI, m$Alpha_CB_UCI),
    check.names = FALSE, stringsAsFactors = FALSE)
}

build_fit <- function(prefix) {
  f  <- fit_master[grepl(prefix, fit_master$Dataset, fixed = TRUE), , drop = FALSE]
  ci <- ci_master[grepl(prefix, ci_master$Dataset, fixed = TRUE), , drop = FALSE]
  m  <- merge(f, ci[, c("Dataset", "RMSEA_LCI", "RMSEA_UCI")], by = "Dataset", sort = FALSE)
  data.frame(
    Dataset               = short_name(m$Dataset),
    `Chi square`          = sprintf("%.2f", m$Chi_Square),
    `p`                   = ifelse(m$P_Value < .001, "<.001", sprintf("%.3f", m$P_Value)),
    CFI                   = sprintf("%.2f", m$CFI),
    TLI                   = sprintf("%.2f", m$TLI),
    `RMSEA [90% CI]`      = sprintf("%.2f [%.3f, %.3f]", m$RMSEA, m$RMSEA_LCI, m$RMSEA_UCI),
    SRMR                  = sprintf("%.2f", m$SRMR),
    BIC                   = sprintf("%.2f", m$BIC),
    check.names = FALSE, stringsAsFactors = FALSE)
}

studies <- list(
  list(table = "Table S2", prefix = "Study1_SUSPECTS_", label = "Study 1"),
  list(table = "Table S5", prefix = "Study2_ACTS_",     label = "Study 2"),
  list(table = "Table S8", prefix = "Study3_CMQ_",      label = "Study 3")
)

for (st in studies) {
  rel <- build_reliability(st$prefix)
  fit <- build_fit(st$prefix)
  stopifnot(nrow(rel) > 0, nrow(fit) > 0)
  # tab_dfs() ignores its own `file` argument in this version of sjPlot and writes nothing,
  # so the HTML it returns is written here instead.
  tt <- tab_dfs(
    list(rel, fit),
    titles = c(paste0(st$table, " (top): reliability, ", st$label,
                      ". Cronbach's alpha with Feldt 95% intervals."),
               paste0(st$table, " (bottom): fit of the two-factor model, ", st$label,
                      ". RMSEA with its 90% interval."))
  )
  target <- file.path(sub_dir, paste0(st$table, ".doc"))
  writeLines(tt$page.complete, con = file(target, encoding = "UTF-8"))
  stopifnot(file.exists(target))
  copied <- c(copied, paste0(st$table, ".doc"))
}
```

# Check the bundle is complete

```{r}
expected <- c(
  paste0("Figure ", 1:4, ".png"),
  paste0("Figure ", 1:4, ".pdf"),
  paste0("Figure S", 1:25, ".png"),
  paste0("Table S", 1:10, ".doc")
)

present <- list.files(sub_dir)
absent  <- setdiff(expected, present)
extra   <- setdiff(present, expected)

cat("files in Output/Submission:", length(present), "of", length(expected), "expected\n")
if (length(missing)) { cat("\nsources that could not be found:\n"); print(missing) }
if (length(absent))  { cat("\nMISSING from the bundle:\n"); print(absent) }
if (length(extra))   { cat("\nunexpected extra files:\n"); print(extra) }
if (!length(absent) && !length(missing)) cat("\nBundle complete.\n")

writeLines(sort(present), file.path(sub_dir, "_contents.txt"))
```
